```{r}
library('ggplot2')
library('latex2exp')
library('coda')
library('rjags')

```

```{r}

```

# Exercise 1

## Point 1
We have that y follows a binomial probability distribution: the method either fails to detect the desease or it fails

## Point 2
```{r}
trials <- 75
new_fails <- 6
```

```{r}
cat('We use as an estimator y/n so, frequqntist estimator of the failure probability = ', new_fails/trials)
```








```{r}
trials <- 75
mean_beta <- 0.15
std_beta <- 0.14
alpha <- ((1-mean_beta)/(std_beta^2) -1/mean_beta)*mean_beta^2
beta <- alpha*(1/mean_beta - 1)
#Setting the alpha parameter to have the mode at 15/75

prior <- function(x) {dbeta(x, shape1 = alpha, shape2 = beta)}

```






```{r}
x_axis <- seq(0,1, length.out=1000)
plot <- ggplot() +
        geom_line(aes(x=x_axis, y=prior(x_axis))) +
        theme_bw() 
plot
```




```{r}
posterior <- function(x) 
{dbeta(x, shape1=alpha + new_fails, shape2 = trials - new_fails + beta)}
```


```{r}


plot <- ggplot() +
        geom_line(aes(x =x_axis, y = posterior(x_axis))) +
        labs(title = 'Posterior of the binomial probability parameter',
             x = 'Prob', y = 'Posterior pdf') +
        theme_bw()

plot
```


## Point 4

### We choose as the null hypothesis the fact that the probability of failing to detect the disease is greater or equal than 15%

```{r}
# Here we visualize the region corresponding to the null hypothesis
plot <- ggplot() +
        geom_line(aes(x_axis, y = posterior(x_axis), color='Posterior')) +
        geom_vline(aes(xintercept = 0.15, color='Prob=0.15'), linetype='dashed',
                   lwd=1) +
        geom_ribbon(aes(x=seq(0.15, 1, 0.01), ymin = 0, 
                        ymax = posterior(seq(0.15, 1, 0.01)
                        )), color='firebrick', fill='green') +
        theme_bw()
plot
```


```{r}
cat(paste('The integral of the region of interest is', 
          round(integrate(posterior, lower=0.15, upper=1)$value, digits = 3)))
```
Having chose the level of significance at $5$ % and being the integral lower then 0.05 we reject the null hyotothesis.

## Point 5

### With the classical method

```{r}
y_vector <- 0:25
p_null <- 0.15

plot <- ggplot() +
        geom_col(aes(x=y_vector, y=dbinom(y_vector, prob = p_null, size = trials)), 
                 fill='blue', alpha=0.5, color='black') +
        geom_col(aes(x=6, y=dbinom(6, prob = p_null, size = trials)), 
                 fill='firebrick', alpha=0.5, color='black') +
        labs(title = 'Frequentist hypothesis testing', x = 'y values', y = 'Posterior values')+
        geom_hline(aes(yintercept=0.05), linetype='dashed', color='magenta') +      
        annotate('text', x=1, y=0.055 , label=sprintf("alpha = %s", 0.05), size=3) +
        theme_bw()  +
        scale_x_discrete(limits = 0:25, labels= 0:25)
  
plot
```
the value lies in the rejection region so we can reject the null hypothesis also with freqerntist's approach

### We choose as the method to use Fischer's method here
```{r}
plot <- ggplot() +
        geom_col(aes(x=0:8, y = pbinom(0:8, size=75, prob=0.15)), fill='blue', alpha=0.3
                 ,color = 'black') +
        geom_col(aes(x=6, y = pbinom(6, size=75, prob=0.15)), fill='green', alpha=0.5) +
        geom_hline(aes(yintercept=0.05), linetype='dashed', color='firebrick') +
        labs(title = 'Fischer\'s method hypothesis testing', x = 'Values of fails', 
             y= 'Cumulative values') +
        theme_bw()
plot

```
```{r}
cat('We have that P(y|n,p) <= 6 =',  pbinom(6, size=75, prob=0.15), '\n
    that is greater than 0.05 so we accept the null hypothesis') 
```


# Exercise 2

We have that in the case of a uniform prior the posterior distribution is a gamma
distribuion with $\alpha = \sum_i y_i + 1$ and $\beta = n$


```{r}
deaths <- 0:5
obs_1 <- c(109, 65, 22, 3, 1, 0)
obs_2 <- c(144, 91, 32, 11, 2, 0)

beta_post <- sum(obs_1 + obs_2)
alpha_post <- sum((obs_1 + obs_2)*deaths) + 1
x_axis <- seq(0.25, 1, 0.001)
posterior <- dgamma(x_axis, shape=alpha_post, scale = 1/beta_post)
cumulative <- pgamma(x_axis, shape=alpha_post, scale = 1/beta_post)
lower_bound <- x_axis[length(cumulative[cumulative <=0.025])]
upper_bound <- x_axis[length(cumulative[cumulative <=0.975])]

axis_ribbon <- seq(lower_bound, upper_bound, 0.001)

plot <- ggplot() +
        geom_line(aes(x=x_axis, y=posterior)) +
        labs(x = TeX('$\\lambda$ values'), y = 'Posterior pdf' , title=TeX('Posterior of the $\\lambda$')) +
        
        theme_bw() +
        theme(plot.title = element_text(hjust =0.5)) +
        geom_vline(aes(xintercept=alpha_post/beta_post), linetype='dashed', color='green')+
        annotate('text', x=alpha_post/beta_post+0.07, y=11 , label=sprintf("Mean = %s", round(alpha_post/beta_post, 3)), size=3) +
        geom_ribbon(aes(x = axis_ribbon, ymin=0, ymax=dgamma(axis_ribbon, shape=alpha_post, scale = 1/beta_post)), fill='blue', alpha=0.3) +
        geom_vline(aes(xintercept = lower_bound, color='Bounds of the \ncredible interval')
                   , linetype = 'dashed') +
        geom_vline(aes(xintercept = upper_bound)
                   , linetype = 'dashed', color='magenta') +
  
        scale_color_manual(values = c('Bounds of the \ncredible interval'='magenta')) 

plot
```


```{r}
cat(paste('The mean computed analitically is:', round(alpha_post/beta_post, 3)))
cat(paste('\nThe confidence interval is: ', round(lower_bound, 3), '-', round(upper_bound, 3)))

median <- x_axis[length(cumulative[cumulative <=0.5])]

cat(paste('\nThe median computed numerically is: ', median))

```

## Point 2 

We have that in the case of Jeffreys’ prior the posterior is a gamma distribution
with $\alpha = \sum_i y_i + \frac{1}{2}$ and $\beta = n$

```{r}
deaths <- c(0, 1, 2, 3, 4, 5)
obs_1 <- c(109, 65, 22, 3, 1, 0)
obs_2 <- c(144, 91, 32, 11, 2, 0)

beta_post <- sum(obs_1 + obs_2)
alpha_post <- sum((obs_1 + obs_2)*deaths) + 1/2
x_axis <- seq(0.25, 1, 0.001)
posterior <- dgamma(x_axis, shape=alpha_post, scale = 1/beta_post)
cumulative <- pgamma(x_axis, shape=alpha_post, scale = 1/beta_post)
lower_bound <- x_axis[length(cumulative[cumulative <=0.025])]
upper_bound <- x_axis[length(cumulative[cumulative <=0.975])]

axis_ribbon <- seq(lower_bound, upper_bound, 0.001)

plot <- ggplot() +
        geom_line(aes(x=x_axis, y=posterior)) +
        labs(x = TeX('$\\lambda$ values'), y = 'Posterior pdf' , title=TeX('Posterior of the $\\lambda$'), color='Legend') +
        
        theme_bw() +
        theme(plot.title = element_text(hjust =0.5)) +
        geom_vline(aes(xintercept=alpha_post/beta_post), linetype='dashed', color='green')+
        annotate('text', x=alpha_post/beta_post+0.07, y=11 , label=sprintf("Mean = %s", round(alpha_post/beta_post, 3)), size=3) +
        geom_ribbon(aes(x = axis_ribbon, ymin=0, ymax=dgamma(axis_ribbon, shape=alpha_post, scale = 1/beta_post)), fill='blue', alpha=0.3) +
        geom_vline(aes(xintercept = lower_bound, color='Bounds of the \nconfidence interval')
                   , linetype = 'dashed') +
        geom_vline(aes(xintercept = upper_bound)
                   , linetype = 'dashed', color='magenta') +
  
        scale_color_manual(values = c('Bounds of the \nconfidence interval'='magenta')) 

plot

```
```{r}
cat(paste('The mean computed analitically is:', round(alpha_post/beta_post, 3)))
cat(paste('\nThe variance computed analitically is:', round(alpha_post/(beta_post^2), 4)))
cat(paste('\nThe confidence interval is: ', round(lower_bound, 3), '-', round(upper_bound, 3)))

median <- x_axis[length(cumulative[cumulative <=0.5])]

cat(paste('\nThe median computed numerically is: ', median))
```

# Exercise 3

## Point 1
```{r}
y <- 11
n<- 116
cat(paste('The frequentist estimator for p is y/n = ', round(y/n, 3)))
```

## Point 2

We have that the posterior in this particulaer beta prior case is again a beta with 
$\alpha' = \alpha + y$ and $\beta' = n - y + \beta$

```{r}
prior <- function(x){dbeta(x, shape1 = 1, shape2 = 2)}
```


```{r}
alpha_post =  1 + y
beta_post = n - y + 10
posterior <- function(x){dbeta(x, shape1 = alpha_post, shape2 = beta_post)}
```


```{r}
x_axis <- seq(0, 1, 0.001)
cumulative <- pbeta(x_axis,  shape1 = alpha_post, shape2 = beta_post)
lower_bound <- x_axis[length(cumulative[cumulative <=0.025])]
upper_bound <- x_axis[length(cumulative[cumulative <=0.975])]
mean <- alpha_post/(beta_post + alpha_post)
mode <- (alpha_post - 1)/(beta_post + alpha_post-2)
axis_ribbon <- seq(lower_bound, upper_bound, 0.001)

plot <- ggplot() +
        geom_line(aes(x=x_axis, y = posterior(x_axis))) +
        geom_vline(aes(xintercept=mean), linetype='dashed', color='green')+
        geom_vline(aes(xintercept=mode), linetype='dashed', color='black') +
        xlim(0, 0.5) +
        theme_bw() +
        labs(title = TeX('Posterior of $p$'), color='Legend', x='Probability values',
             y='Posterior pdf') +
        theme(plot.title = element_text(hjust = 0.5)) +
        annotate('text', x=mode-0.05, y=16 , label=sprintf("Mode = %s", round(mode, 3)), size=3) +
        annotate('text', x=mode+0.05, y=16 , label=sprintf("Mean = %s", round(mean, 3)), size=3) +
        geom_ribbon(aes(x = axis_ribbon, ymin=0, ymax=posterior(axis_ribbon)), fill='blue', alpha=0.3) +
        geom_vline(aes(xintercept = lower_bound, color='Bounds of the \ncredible interval')
                   , linetype = 'dashed') +
        geom_vline(aes(xintercept = upper_bound)
                   , linetype = 'dashed', color='magenta') +
        scale_color_manual(values = c('Bounds of the \ncredible interval'='magenta')) 
        

plot
```
```{r}
cat(paste('We choose the mode as the estimator, \nits value, computed analitically, is:', round(mode, 3)))
cat(paste('\n\nThe mean computed analitically is:', round(mean, 3)))
cat(paste('\nThe bounds of the credible interval are:', 
          round(lower_bound, 4), '-', round(upper_bound, 4)))
variance <- (alpha_post*beta_post)/((alpha_post +beta_post)^2*(alpha+beta+1))

cat(paste('\nThe variance computed analitically is:', round(variance, 4)))

```

## Point 4

We begin with the frequentist approach

```{r}
y_vector <- 0:25
p_null <- 0.1

plot <- ggplot() +
        geom_col(aes(x=y_vector, y=dbinom(y_vector, prob = p_null, size = n)), 
                 fill='blue', alpha=0.5, color='black') +
        geom_col(aes(x=11, y=dbinom(11, prob = p_null, size = n)), 
                 fill='firebrick', alpha=0.5, color='black') +
        labs(title = 'Frequentist hypothesis testing', x = 'y values', y = 'Posterior values')+
        geom_hline(aes(yintercept=0.05), linetype='dashed', color='magenta') +      
        annotate('text', x=1, y=0.055 , label=sprintf("alpha = %s", 0.05), size=3) +
        theme_bw()  +
        scale_x_discrete(limits = 0:25, labels= 0:25)
  
plot


```
### 

```{r}
cat(paste('We see that $y=11$ is in the acceptance region, \nthen we do not reject the null hypothesis, infact the value at y = 11 is:', round(dbinom(11, prob = p_null, size = n),3), '> 0.05'))
```

We look now if we keep the null hypothesis also with the p-value
```{r}
p_value <- round(pbinom(11, size= n, prob = p_null)+1-pbinom(n-11-1, n, p_null), 4)

cat(paste('The p-value is:', p_value, '> 0.05'))
```

So we keep the null hypothesis also with Fischer's method

### Bayesian approach
```{r}
cat(paste('We\'ve already computed the posterior previously, we obtained the
following credible interval: ', lower_bound, '-', upper_bound))

cat('\n0.1 is inside the credible interval then we do not reject the null hypothesis')
```

```{r}
# Visual representation of the previous result

plot <- ggplot() +
        geom_line(aes(x=x_axis, y = posterior(x_axis))) +
        xlim(0, 0.5) +
        theme_bw() +
        geom_vline(aes(xintercept = 0.1), color='green', linetype = 'dashed') +
        labs(title = TeX('Bayesian hypothesis testing'), color='Legend', x='Probability values',
             y='Posterior pdf') +
        theme(plot.title = element_text(hjust = 0.5)) +
        annotate('text', x=mode+0.04, y=16 , label=sprintf("p = %s", 0.1, size=2)) +
        geom_ribbon(aes(x = axis_ribbon, ymin=0, ymax=posterior(axis_ribbon)), fill='blue', alpha=0.3) +
        geom_vline(aes(xintercept = lower_bound, color='Bounds of the \ncredible interval')
                   , linetype = 'dashed') +
        geom_vline(aes(xintercept = upper_bound)
                   , linetype = 'dashed', color='magenta') +
        scale_color_manual(values = c('Bounds of the \ncredible interval'='magenta')) 
        

plot

```

## Point 5

```{r}
y <- 9
n <- 165

cat(paste('The frequentist estimator for p is y/n = ', round(y/n, 3)))
```

## Point 6
In this point we exploit the fact the with a beta prior the posterior is still a
beta with $\alpha'=\alpha + y$ and $\beta' = n - y + \beta$
### First prior
```{r}
y <- 9
n <- 165
alpha_post <- y + 1
beta_post <- n - y + 10
# with beta(1, 10) as the prior
posterior <- function(x){dbeta(x, shape1 = alpha_post, shape2 = beta_post)}
```


```{r}
x_axis <- seq(0, 1, 0.001)
cumulative <- pbeta(x_axis,  shape1 = alpha_post, shape2 = beta_post)
lower_bound <- x_axis[length(cumulative[cumulative <=0.025])]
upper_bound <- x_axis[length(cumulative[cumulative <=0.975])]
mean <- alpha_post/(beta_post + alpha_post)
mode <- (alpha_post - 1)/(beta_post + alpha_post-2)
axis_ribbon <- seq(lower_bound, upper_bound, 0.001)

plot <- ggplot() +
        geom_line(aes(x=x_axis, y = posterior(x_axis))) +
        geom_vline(aes(xintercept=mean), linetype='dashed', color='green')+
        geom_vline(aes(xintercept=mode), linetype='dashed', color='black') +
        xlim(0, 0.3) +
        theme_bw() +
        labs(title = TeX('Posterior of $p$'), color='Legend', x='Probability values',
             y='Posterior pdf') +
        theme(plot.title = element_text(hjust = 0.5)) +
        annotate('text', x=mode-0.03, y=25 , label=sprintf("Mode = %s", round(mode, 3)), size=3) +
        annotate('text', x=mode+0.03, y=25 , label=sprintf("Mean = %s", round(mean, 3)), size=3) +
        geom_ribbon(aes(x = axis_ribbon, ymin=0, ymax=posterior(axis_ribbon)), fill='blue', alpha=0.3) +
        geom_vline(aes(xintercept = lower_bound, color='Bounds of the \ncredible interval')
                   , linetype = 'dashed') +
        geom_vline(aes(xintercept = upper_bound)
                   , linetype = 'dashed', color='magenta') +
        scale_color_manual(values = c('Bounds of the \ncredible interval'='magenta')) 
        

plot
```

```{r}
cat(paste('We choose the mode as the estimator, \nits value, computed analitically, is:', round(mode, 3)))
cat(paste('\n\nThe mean computed analitically is:', round(mean, 3)))
cat(paste('\nThe bounds of the credible interval are:', 
          round(lower_bound, 4), '-', round(upper_bound, 4)))
variance <- (alpha_post*beta_post)/((alpha_post +beta_post)^2*(alpha+beta+1))

cat(paste('\nThe variance computed analitically is:', round(variance, 3)))
```

## Second prior
```{r}
alpha_prior <- 12
beta_prior <- 115
alpha_post <-  y + alpha_prior
beta_post <- n - y + beta_prior

# with previous posterior as the prior
posterior <- function(x){dbeta(x, shape1 = alpha_post, shape2 = beta_post)}
```


```{r}
cumulative <- pbeta(x_axis,  shape1 = alpha_post, shape2 = beta_post)
lower_bound <- x_axis[length(cumulative[cumulative <=0.025])]
upper_bound <- x_axis[length(cumulative[cumulative <=0.975])]
mean <- alpha_post/(beta_post + alpha_post)
mode <- (alpha_post - 1)/(beta_post + alpha_post-2)
axis_ribbon <- seq(lower_bound, upper_bound, 0.001)

plot <- ggplot() +
        geom_line(aes(x=x_axis, y = posterior(x_axis))) +
        geom_vline(aes(xintercept=mean), linetype='dashed', color='green')+
        geom_vline(aes(xintercept=mode), linetype='dashed', color='black') +
        xlim(0, 0.3) +
        theme_bw() +
        labs(title = TeX('Posterior of $p$'), color='Legend', x='Probability values',
             y='Posterior pdf') +
        theme(plot.title = element_text(hjust = 0.5)) +
        annotate('text', x=mode-0.03, y=27 , label=sprintf("Mode = %s", round(mode, 3)), size=3) +
        annotate('text', x=mode+0.03, y=27 , label=sprintf("Mean = %s", round(mean, 3)), size=3) +
        geom_ribbon(aes(x = axis_ribbon, ymin=0, ymax=posterior(axis_ribbon)), fill='blue', alpha=0.3) +
        geom_vline(aes(xintercept = lower_bound, color='Bounds of the \ncredible interval')
                   , linetype = 'dashed') +
        geom_vline(aes(xintercept = upper_bound)
                   , linetype = 'dashed', color='magenta') +
        scale_color_manual(values = c('Bounds of the \ncredible interval'='magenta')) 
        

plot

```
```{r}
cat(paste('We choose the mode as the estimator, \nits value, computed analitically, is:', round(mode, 3)))
cat(paste('\n\nThe mean computed analitically is:', round(mean, 3)))
cat(paste('\nThe bounds of the credible interval are:', 
          round(lower_bound, 4), '-', round(upper_bound, 4)))
variance <- (alpha_post*beta_post)/((alpha_post +beta_post)^2*(alpha+beta+1))

cat(paste('\nThe variance computed analitically is:', round(variance, 4)))
```
## Point 8
### Frequentist approach

```{r}
y_vector <- 0:30
p_null <- 0.1

plot <- ggplot() +
        geom_col(aes(x=y_vector, y=dbinom(y_vector, prob = p_null, size = n)), 
                 fill='blue', alpha=0.5, color='black') +
        geom_col(aes(x=9, y=dbinom(9, prob = p_null, size = n)), 
                 fill='firebrick', alpha=0.5, color='black') +
        labs(title = 'Frequentist hypothesis testing', x = 'y values', y = 'Posterior values')+
        geom_hline(aes(yintercept=0.05), linetype='dashed', color='magenta') +      
        annotate('text', x=1, y=0.055 , label=sprintf("alpha = %s", 0.05), size=3) +
        theme_bw()  +
        scale_x_discrete(limits = 0:30, labels= 0:30)
  
plot
```

```{r}
cat(paste('We have that y = 9 lies in the acceptance region: ',
          round(dbinom(9, prob = p_null, size = n),3), '<', 0.05))
```

We thus have that we can reject the null hypothesis

```{r}
# With Fischer's method

p_value <- round(pbinom(9, size= n, prob = p_null)+1-pbinom(n-9-1, n, p_null), 3)

cat(paste('The p-value is:', p_value, '< 0.05'))
```

So using Fischer's method leads us to the same outcome

### Bayesian hypothesis testing

**Looking back at the credible intervals previously computed we can see that using the posterior of the first experiment as the prior we obtained the credibility interval 0.045-0.104 so we cannot reject the null hypothesis**

**Using the beta(1, 10) as the prior we obtained as the credibility interval 0.027 - 0.095 so in this case we can reject the null hypothesis**


# Exercise 4

```{r}
sucesses <- 6
n <- 75
data_obs <- rep(c(1, 0), c(sucesses, n-sucesses))

data <- NULL
data$X <- data_obs
data$n <- length(data_obs)
```


```{r}
model <- 'ex_1.bug'
jm <- jags.model(model, data)
update(jm, 1000)
chain <- coda.samples(jm, c("p"), n.iter=10000)
s <- (summary(chain))
print(s)
```



```{r}
plot(chain, col="navy")
```

```{r}
chain_df <- as.data.frame( as.mcmc(chain) )
head(chain_df)
```
```{r}
trials <- 75
mean_beta <- 0.15
std_beta <- 0.14
alpha <- ((1-mean_beta)/(std_beta^2) -1/mean_beta)*mean_beta^2
beta <- alpha*(1/mean_beta - 1)
posterior <- function(x) 
{dbeta(x, shape1=alpha + new_fails, shape2 = trials - new_fails + beta)}

x_axis <- seq(0,0.3,0.001)


plot <- ggplot() +
        geom_histogram(aes(chain_df$p, y=..density.., fill='Chain'), color='black', bins=100) +
        geom_line(aes(x =x_axis, y = posterior(x_axis), color='Analytical posterior'), lwd=1.5)+
        scale_color_manual(values = c('Analytical posterior'='blue')) +
        labs(color='Legend', fill='', x='Probability values', y = 'Posterior pdf',
             title = 'MCMC inference') +
        
        theme_bw()

plot
```

```{r}
stat_values <- s$statistics
cat(paste('The mean given by the chain is', round(stat_values[['Mean']], 4)))
cat(paste('\nThe standard deviation given by the chain is', round(stat_values[['SD']], 4)))
cat(paste('\nThe median given by the chain is', round(s$quantiles[['50%']], 4)))
cat(paste('\nThe confidence interval given by the chain is', round(s$quantiles[['2.5%']], 4),
          '-', round(s$quantiles[['97.5%']], 4)))
```

# Exercise 5

```{r}
n <- obs_1 + obs_2
obs <- rep(deaths, n)


```


```{r}

data <- NULL
data$X <- obs

```

```{r}
model <- 'ex_2.bug'
jm <- jags.model(model, data)
update(jm, 1000)
chain <- coda.samples(jm, c("lambda"), n.iter=10000)
s <- (summary(chain))
print(s)

```
```{r}
plot(chain, col="navy")
```

```{r}
chain_df <- as.data.frame( as.mcmc(chain) )
head(chain_df)
```

```{r}
x_axis <- seq(0.3, 1, 0.001)
beta_post <- sum(obs_1 + obs_2)
alpha_post <- sum((obs_1 + obs_2)*deaths) + 1
posterior <- dgamma(x_axis, shape=alpha_post, scale = 1/beta_post)

plot <- ggplot() +
        geom_histogram(aes(chain_df$lambda, y=..density.., fill='Chain'), color='black', bins=100) +
         geom_line(aes(x =x_axis, y = posterior, color='Analytical posterior'), lwd=1) +
           
        scale_color_manual(values = c('Analytical posterior'='blue')) +
        labs(color='Legend', fill='', x=TeX('$\\lambda$ values'), y = 'Posterior pdf',
             title = 'MCMC inference poisson process') +
        
        theme_bw()



plot
```
```{r}
stat_values <- s$statistics
cat(paste('The mean given by the chain is', round(stat_values[['Mean']], 4)))
cat(paste('\nThe standard deviation given by the chain is', round(stat_values[['SD']], 4)))
cat(paste('\nThe median given by the chain is', round(s$quantiles[['50%']], 4)))
cat(paste('\nThe confidence interval given by the chain is', round(s$quantiles[['2.5%']], 4),
          '-', round(s$quantiles[['97.5%']], 4)))
```
### Jeffreys prior

```{r}
model <- 'ex_2_b.bug'
jm <- jags.model(model, data)
update(jm, 1000)
chain <- coda.samples(jm, c("lambda"), n.iter=10000)
s <- (summary(chain))
print(s)

```
```{r}
plot(chain, col="navy")
```

```{r}
beta_post <- sum(obs_1 + obs_2)
alpha_post <- sum((obs_1 + obs_2)*deaths) + 1/2
posterior <- dgamma(x_axis, shape=alpha_post, scale = 1/beta_post)

plot <- ggplot() +
        geom_histogram(aes(chain_df$lambda, y=..density.., fill='Chain'), color='black', bins=100) +
         geom_line(aes(x =x_axis, y = posterior, color='Analytical posterior'), lwd=1) +
           
        scale_color_manual(values = c('Analytical posterior'='blue')) +
        labs(color='Legend', fill='', x=TeX('$\\lambda$ values'), y = 'Posterior pdf',
             title = 'MCMC inference Jeffreys prior') +
        
        theme_bw()



plot
```
```{r}
stat_values <- s$statistics
cat(paste('The mean given by the chain is', round(stat_values[['Mean']], 4)))
cat(paste('\nThe standard deviation given by the chain is', round(stat_values[['SD']], 4)))
cat(paste('\nThe median given by the chain is', round(s$quantiles[['50%']], 4)))
cat(paste('\nThe confidence interval given by the chain is', round(s$quantiles[['2.5%']], 4),
          '-', round(s$quantiles[['97.5%']], 4)))
```


```{r}
sucesses <- 11
n <- 116
data_obs <- rep(c(1, 0), c(sucesses, n-sucesses))

data <- NULL
data$X <- data_obs
data$n <- length(data_obs)
```


```{r}
model <- 'ex_1.bug'
jm <- jags.model(model, data)
update(jm, 1000)
chain <- coda.samples(jm, c("p"), n.iter=10000)
s <- (summary(chain))
print(s)
```



```{r}
plot(chain, col="navy")
```

```{r}
chain_df <- as.data.frame( as.mcmc(chain) )
head(chain_df)
```

```{r}
alpha_post =  1 + sucesses
beta_post = n - sucesses + 10
posterior <- function(x){dbeta(x, shape1 = alpha_post, shape2 = beta_post)}
x_axis <- seq(0, 0.3, 0.001)

plot <- ggplot() +
        geom_histogram(aes(chain_df$p, y=..density.., fill='Chain'), color='black', bins=100) +
        geom_line(aes(x =x_axis, y = posterior(x_axis), color='Analytical posterior'), lwd=1.5)+
        scale_color_manual(values = c('Analytical posterior'='blue')) +
        labs(color='Legend', fill='', x='Probability values', y = 'Posterior pdf',
             title = 'MCMC inference') +
        
        theme_bw()

plot
```

```{r}
stat_values <- s$statistics
cat(paste('The mean given by the chain is', round(stat_values[['Mean']], 4)))
cat(paste('\nThe standard deviation given by the chain is', round(stat_values[['SD']], 4)))
cat(paste('\nThe median given by the chain is', round(s$quantiles[['50%']], 4)))
cat(paste('\nThe confidence interval given by the chain is', round(s$quantiles[['2.5%']], 4),
          '-', round(s$quantiles[['97.5%']], 4)))
```

